### 2023-10-17 main.tex
Bozza 2

\begin{align*}
R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
	\\&
	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
	\\&
	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
 \\=&\sum_{r^{x}\in \Omega_{x}}
	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
	\\=&
	\left(E_{ba}^{x}\right)^{T}
\end{align*}
where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
\end{comment}
\paragraph{Elements of the duality matrix.}
Consider the matrix $D$ defined in \eqref{dualityMatrix}.
We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
\begin{equation}\label{proofDualityElements}
\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
\end{equation}
Fix an arbitrary site $x\in V$, then we have that 
\begin{align*}
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
\end{align*}
where we used \eqref{transpositionPropertyR}. \\
On one hand, on the extra-site $u(x)$ we have 
\begin{align*}
\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
\end{align*}
where  we used the orthogonality relation \eqref{ortho}. 
On the other hand, on the site $x$, we have 
\begin{align*}
&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\ldots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
\\&
\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
%\\&=
%\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
%\\&
%\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\cdots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\cdots(n_{N-1}^{x}-k_{N-1})!}
\\& 
\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
\end{align*}
where we used the definitions of the action of $E_{ab}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
\begin{flushright}
    $\square$
\end{flushright}

@@

% However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
 \begin{flushright}
     $\square$
 \end{flushright}
 \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$. % that we connect to every site $x\in V$ of the graph $G$. \\
 Considering $A,B\in gl(N)$, the Hadamard formula reads 
 \begin{equation}\label{HadamardFormula}
     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
 \end{equation}
In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra $gl(N)$ with $c,d\in\{1,\ldots,N\}$. Therefore we compute 
\begin{align}
	\left[B,A\right]=\sum_{a=1}^{N-1}\left[E_{aN},E_{cd}\right]=\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-(1-\delta_{dN})E_{cN}
\end{align}
and 
\begin{align}
	\left[B\left[B,A\right]\right]=&\left[\sum_{a=1}^{N-1}E_{aN},\delta_{cN}\sum_{b=1}^{N-1}E_{bd}-\delta_{d<N}E_{cN}\right]\nonumber\\=&
	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bd}\right]-\delta_{d<N}\left[E_{aN},E_{cN}\right]\right)\nonumber\\=&
	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-\delta_{d<N}\delta_{cN}E_{aN}\right)\nonumber\\=&
	-\left(\delta_{cN}\delta_{d<N}+\delta_{d<N}\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
	\\=&
	-2\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}
\end{align}
From the third commutator on we always obtain zero, i.e. $[B,[B,[B,A]]]=0$. All in all we have that 
 \begin{align}\label{HT-BA}
 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+\delta_{d<N}E_{cN}-\delta_{cN}\delta_{d<N}\sum_{b=1}^{N-1}E_{bN}\dt
 \end{align}
\begin{comment}
\begin{enumerate}
    \item for $A=E_{b N}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT_El1}
        \exp{(-E)}E_{b N}\exp{(E)}=E_{b N}
    \end{equation}
    because $E_{b N}$ commutes with $E$
    \item for $A=E_{bb}$ with $b \in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT_Ell}
        \exp{(-E)}E_{b b}\exp{(E)}=E_{b b}+E_{b N}
    \end{equation}
Indeed, using \eqref{eq:comgl} we have 
    \begin{equation}
       \left[E, E_{bb}\right]=\sum_{a=1}^{N-1}\left(E_{ab}\delta_{b N}-E_{b N}\delta_{ab}\right)=-E_{bN}
    \end{equation}
    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
    \item for $A=E_{Nb}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT-E1l}
        \exp{(-E)}E_{N a}\exp{(E)}=E_{Na}+E_{NN}-\sum_{c=1}^{N-1}\left(E_{cN}+E_{ca}\right)
    \end{equation}
  %\com{Why indices have names $b, k, j, a, b$? Fix one set for the generators}

@@

@@

where, in the up to last equality, we performed a change of summation variable and where in the last equality we used the fact that  
&\sum_{\xi_{a}^{u(x)}=0}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}
Indeed, as a consequence of \eqref{bosonicKX} we have 

@@

Therefore, inserting this last equation in \eqref{siteHadamardII} we obtain 

@@

We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$. Consider an arbitrary initial configuration of $(\bm{n}(t))_{t\geq 0}$ denoted by $\bm{n}$. For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\sum_{k=1}\delta_{s_{k}}^{y_{k}}$ with $y_{k}\in\{1,\ldots,L\}$ and $s_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$. The following  equalities holds thanks to the duality relation \eqref{duality-expectation}:
\\ Already for two-point correlations the computations become more involving and hard to solve. In the following we specialize the chain to the integrable case $\nu=1$. As it will be shown, in such a situation the non-equilibrium steady state correlations can be computed with different techniques exploiting the integrability of the process (matrix product ansatz and quantum inverse scattering method) combined with duality and, as a by-product, all absorption probabilities can be explicitly found. 
\subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}. We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. Now we assume the hard-core exclusion rule, i.e. $\nu=1$. The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$. Duality result stated in Subsection \ref{statementDualitySubsection} can be adapted. The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
\begin{equation}\label{transpostionPropertyFund}
	e_{ab}^T= e_{ba}\dt
Therefore, duality matrix reads
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\otimes \mathcal{D}_{L+1}
where $\mathcal{D}_{0}$ and $\mathcal{D}_{L+1}$ are given in \eqref{dualityMatrix2}. 
The elements of this duality matrix are given by
\begin{equation}\label{ElementsDualityMatrixChain}
	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
The dual Hamiltonian is
	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
\begin{equation}\label{boundary-H-dual-chain}
	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,E_{Na}^{1}-E_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,E_{Na}^{L}-E_{aa}^{L}\right)\dt
In the long-time limit the dual process voids the chain, i.e. all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$. We also notice that, up the the bosonic creation operators $(a^{\dagger})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular. This simplification will be crucial in Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping}.\\

>>>>

\begin{align*}
R_{x}E_{ab}^{x}R_{x}^{-1}=&\sum_{r^{x}\in\Omega_{x}}\frac{\xi_{1}^{x}!\ldots r_{N}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots, \xi_{N}^{x}|
	\\&
	\sum_{s^{x}\in \Omega_{x},}s_{b}^{x}|s_{1}^{x},\ldots,s_{a}^{x}+1,\ldots,s_{b}^{x}-1,\ldots s_{N}^{x}\rangle \langle s_{1}^{x},\ldots,s_{N}^{x}|
	\\&
	\sum_{n^{x}\in\Omega_{x}}\frac{\nu!}{n_{1}!\ldots n_{N}!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle \langle n_{1}^{x},\ldots, n_{N}^{x}|
 \\=&\sum_{r^{x}\in \Omega_{x}}
	\xi_{a}^{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \langle \xi_{1}^{x},\ldots,\xi_{a}^{x}-1,\ldots,r_{b}^{x}-1,\ldots,\xi_{N}^{x}|
	\\=&
	\left(E_{ba}^{x}\right)^{T}
\end{align*}
where in the up to last equation we used the orthogonality relation \eqref{ortho}. 
\end{comment}
\paragraph{Elements of the duality matrix.}
Consider the matrix $D$ defined in \eqref{dualityMatrix}.
We aim to show that its matrix elements coincide with duality function \eqref{dualityElements}, i.e.
\begin{equation}\label{proofDualityElements}
\langle \bm{n}|D|\bm{\xi}\rangle=D(\bm{n},\bm{\xi})\qquad   \forall \bm{n}\in \Omega,\quad \bm{\xi}\in \widetilde{\Omega}\,.
\end{equation}
Fix an arbitrary site $x\in V$, then we have that 
\begin{align*}
	 &\langle n^{x}|d_{x}\otimes \dd|\xi^{x}\rangle\\=&\langle n_{1}^{x},\ldots,n_{N}^{x}| (\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x}}))^{T}R_{x}\otimes\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|
	 \\&|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle \otimes |\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle
\end{align*}
where we used \eqref{transpositionPropertyR}. \\
On one hand, on the extra-site $u(x)$ we have 
\begin{align*}
\sum_{q_{1}^{u(x)},\ldots,q_{N-1}^{u(x)}=0}^{\infty}\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{q_{a}^{u(x)}}\langle q_{1}^{u(x)},\ldots,q_{N}^{u(x)}|\xi_{1}^{u(x)},\ldots,\xi_{N}^{u(x)}\rangle=\prod_{a=1}^{N-1}\left(\rho_{a}^{x}\right)^{\xi_{a}^{u(x)}}
\end{align*}
where  we used the orthogonality relation \eqref{ortho}. 
On the other hand, on the site $x$, we have 
\begin{align*}
&\langle n_{1}^{x},\ldots,n_{N}^{x}|(\exp{(E_{N1}^{x}+\ldots+E_{N\,N-1}^{x})})^{T}R_{x}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle\\&= \langle  n_{1}^{x},\ldots,n_{N}^{x}|\left(\sum_{k_{1}=0}^{\infty}\frac{\left\{\left(E_{N1}^{x}\right)^{T}\right\}^{k_{1}}}{k_{1}!}\ldots\sum_{k_{N-1}=0}^{\infty}\frac{\left\{\left(E_{N\,N-1}^{x}\right)^{T}\right\}^{k_{N-1}}}{k_{N-1}!}\sum_{s\in\Omega_{x}}\frac{s_{1}^{x}!\cdots s_{N}^{x}!}{\nu!}|s_{1}^{x},\ldots,s_{N}^{x}\rangle\langle s_{1}^{x},\ldots,s_{N}^{x}|\right)
\\&
\hspace{2.cm}\qquad|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
%\\&=
%\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},n_{N}^{x}+k_{1}+\ldots+k_{N-1}|
%\\&
%\hspace{2.cm}\prod_{a=1}^{N-1}\left((n_{a}^{x}(n_{a}^{x}-1)\ldots (n_{a}^{x}-k_{a}+1)\right)\frac{1}{k_{1}!,\ldots,k_{N-1}!}\frac{\xi_{1}^{x}!\ldots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\sum_{k_{1}=0}^{n_{1}^{x}}\ldots\sum_{k_{N-1}=0}^{n_{N-1}^{x}}\langle n_{1}^{x}-k_{1},\ldots,n_{N-1}^{x}-k_{N-1},\ldots,n_{N}^{x}+k_{1}+\ldots+k_{N-1}|\frac{n_{1}^{x}!\cdots n_{N-1}^{x}!}{(n_{1}^{x}-k_{1})!\cdots(n_{N-1}^{x}-k_{N-1})!}
\\& 
\hspace{2.cm}\qquad\frac{1}{k_{1}!\cdots k_{N-1}!}\frac{\xi_{1}^{x}!\cdots \xi_{N}^{x}!}{\nu!}|\xi_{1}^{x},\ldots,\xi_{N}^{x}\rangle
\\&=
\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
\end{align*}
where we used the definitions of the action of $E_{ab}$  and the orthogonality relations \eqref{ortho}, together with the fact that $\xi_{N}^{x}=\nu-\sum_{a=1}^{N-1}\xi_{a}^{x}$. 
Finally, by taking the product over $x\in V$ \eqref{proofDualityElements} is proved.
\begin{flushright}
    $\square$
\end{flushright}

@@

% However, they would lead to duality matrices where the number of dual particles is greater than the number of original ones, loosing the simplification of the dynamics of the dual process. 
 \begin{flushright}
     $\square$
 \end{flushright}
 \paragraph{Proof of boundary duality \eqref{siteDualRelation}.} To prove \eqref{siteDualRelation} we need to transform via the Hadamard formula the transposed of the site Hamiltonian \eqref{siteDualHamiltonian} and then to  introduce properly a creation operator acting on an extra-site $u(x)$. % that we connect to every site $x\in V$ of the graph $G$. \\
 Considering $A,B\in gl(N)$, the Hadamard formula reads 
 \begin{equation}\label{HadamardFormula}
     \exp{(-B)}A\exp{(B)}=A-\left[B,A\right]+\frac{1}{2!}\left[B,\left[B,A\right]\right]-\frac{1}{3!}\left[B,\left[B,\left[B,A\right]\right]\right]+\ldots
 \end{equation}
In the following we need the application of this with $B=\sum_{a=1}^{N-1}E_{aN}$ defined in \eqref{EquationEx} and with $A$ equal to some of the generator $E_{cd}$ of the Lie algebra $gl(N)$ with $c,d\in\{1,\ldots,N\}$. Therefore we compute 
\begin{align}
	\left[B,A\right]=\sum_{a=1}^{N-1}\left[E_{aN},E_{cd}\right]=\delta_{cN}\sum_{a=1}^{N-1}E_{ad}-(1-\delta_{dN})E_{cN}
\end{align}
and 
\begin{align}
	\left[B\left[B,A\right]\right]=&\left[\sum_{a=1}^{N-1}E_{aN},\delta_{cN}\sum_{b=1}^{N-1}E_{bd}-(1-\delta_{dN})E_{cN}\right]\nonumber\\=&
	\sum_{a=1}^{N-1}\left(\delta_{cN}\sum_{b=1}^{N-1}\left[E_{aN},E_{bd}\right]-(1-\delta_{dN})\left[E_{aN},E_{cN}\right]\right)\nonumber\\=&
	\sum_{a=1}^{N-1}\left(-\delta_{cN}\delta_{ad}\sum_{b=1}^{N-1}E_{bN}-(1-\delta_{dN})\delta_{cN}E_{aN}\right)\nonumber\\=&
	-\left(\delta_{cN}(1-\delta_{dN})+(1-\delta_{dN})\delta_{cN}\right)\sum_{b=1}^{N-1}E_{bN}\nonumber
	\\=&
	-2\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}
\end{align}
From the third commutator on we always obtain zero, i.e. $[B,[B,[B,A]]]=0$. All in all we have that 
 \begin{align}\label{HT-BA}
 	\exp{\left(-\sum_{a=1}^{N-1}E_{aN}\right)}E_{cd}\exp{\left(\sum_{a=1}^{N-1}E_{aN}\right)}=E_{cd}-\delta_{cN}\sum_{a=1}^{N-1}E_{ad}+(1-\delta_{dN})E_{cN}-\delta_{cN}(1-\delta_{dN})\sum_{b=1}^{N-1}E_{bN}\dt
 \end{align}
\begin{comment}
\begin{enumerate}
    \item for $A=E_{b N}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT_El1}
        \exp{(-E)}E_{b N}\exp{(E)}=E_{b N}
    \end{equation}
    because $E_{b N}$ commutes with $E$
    \item for $A=E_{bb}$ with $b \in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT_Ell}
        \exp{(-E)}E_{b b}\exp{(E)}=E_{b b}+E_{b N}
    \end{equation}
Indeed, using \eqref{eq:comgl} we have 
    \begin{equation}
       \left[E, E_{bb}\right]=\sum_{a=1}^{N-1}\left(E_{ab}\delta_{b N}-E_{b N}\delta_{ab}\right)=-E_{bN}
    \end{equation}
    Inserting the above commutator in \eqref{HadamardFormula}, we obtain \eqref{HT_Ell}.
    \item for $A=E_{Nb}$ with $b\in \{1,\ldots,N-1\}$, we obtain 
    \begin{equation}\label{HT-E1l}
        \exp{(-E)}E_{N a}\exp{(E)}=E_{Na}+E_{NN}-\sum_{c=1}^{N-1}\left(E_{cN}+E_{ca}\right)
    \end{equation}
  %\com{Why indices have names $b, k, j, a, b$? Fix one set for the generators}

@@

\begin{equation}\label{extra-site-trick}

@@

where, in the up to last equality, we performed a change of summation variable and we used the fact that  
&\sum_{\xi_{a}^{u(x)}=0}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}+\langle \xi_{1}^{u(x)},\ldots,0,\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\\=&\sum_{\xi_{a}^{u(x)}=1}^{\infty}\rho_{a}^{\xi_{a}^{u(x)}}\langle \xi_{1}^{u(x)},\ldots,\xi_{a}^{u(x)},\ldots,\xi_{N}^{u(x)}|(A^{\dagger})_{a}^{u(x)}\dt
This is a consequence of 

@@

that follows from \eqref{bosonicKX}. Therefore, inserting \eqref{extra-site-trick} in \eqref{siteHadamardII} we obtain 

@@

\subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}. We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. Now we assume the hard-core exclusion rule, i.e. $\nu=1$. The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$. Duality result stated in Subsection \ref{statementDualitySubsection} can be adapted. The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
\begin{equation}\label{transpostionPropertyFund}
	e_{ab}^T= e_{ba}\dt
\end{equation}
Therefore, duality matrix reads
\begin{equation}
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\otimes \mathcal{D}_{L+1}
\end{equation}
where $\mathcal{D}_{0}$ and $\mathcal{D}_{L+1}$ are given in \eqref{dualityMatrix2}. 
The elements of this duality matrix are given by
\begin{equation}\label{ElementsDualityMatrixChain}
	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
\end{equation}
The dual Hamiltonian is
\begin{equation}
	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
\end{equation}
where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
\begin{equation}\label{boundary-H-dual-chain}
	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((a^{\dagger})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
\end{equation}
In the long-time limit the dual process voids the chain, i.e. all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$. We also notice that, up the the bosonic creation operators $(a^{\dagger})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular. This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\

Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. Consider a dual configuration $\bm{\hat{\xi}}:=\sum_{k=1}^{m}\delta_{s_{k}}^{y_{k}}$ where $s_{k}\in\{1,\ldots,N-1\}$ and $y_{k}\in\{1,\ldots,L\}$ such that $y_{k}<y_{k+1}$ for every $k\in\{1,\ldots,m\}$. Fix an arbitrary initial configuration $\bm{n}$, the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\bm{\hat{\xi}}$ read
\begin{equation}
	D(\bm{n},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{n_{s_{k}}^{s_{k}}=1\}}\dt
\end{equation}
Denoting the $m$-point correlations by $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}$ we have 
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}}\rangle_{stat}&=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\hat{\xi}}(t))\right]
	\\&=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
\end{split}
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{k}\delta_{0}+(1-c_{k})\delta_{L+1}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
\end{equation}
 namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $s_{k}$ at site $y_{k}$ are absorbed at left and $1-c_{k}$ of the same particles absorbed at right. Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.
